Geometric variational problems

### 2020-11-16 NSF2020/Description/newspecificaim3.tex
RJR

\subsubsection{Electromechanical effects on the dynamic assembly of amphiphiles \label{subsubsec:em_effects}}
Using flicker spectroscopy of the shape fluctuations of a giant
unilamellar vesicle (GUV), the bending rigidity is determined as a
function of lipid composition from 0 to 100 mol $\%$ of charged lipids
in recent experiments~\cite{FaizEtAl2019_SoftMatt}---membrane bending
rigidity increases with lipid surface charge, while decreases with salt
in the bulk due to the screening of the lipid surface charge. This
agrees with several theoretical models~\cite{Kralchevsky1996_JCIS,
May1996_JChemPhys, LoubetEtAl2013_PRE} that also assume the quadratic
form of the elastic energy density in the presence of surface charge and
bulk charge~\cite{DuplantierGoldstein1990_PRL, Winterhalter1992_JPC}. As
the electrostatic interaction is non-local in nature, we expect that the
controversy of the HK elastic energy form (see
\S\ref{subsec:specific_aim_1}) would be worse in the presence of
electrostatic interactions and electrokinetics. The PIs will extend
the approaches in \S\ref{subsec:specific_aim_1} to charged lipids to
calculate the bending moduli and compare against the experimental
results in~\cite{FaizEtAl2019_SoftMatt}. We propose to incorporate an
explicit surface charge on each particle boundary $P_i$ and compute the
electrostatic potential as a functional of particle configuration.
Adding the electrostatic forces to the hydrophobic attraction forces
between particles to compute the particle assembly dynamics, we can then
calculate elastic moduli as outlined in \S\ref{subsec:specific_aim_1}.
Results from these proposed calculations provide further comparisons and
validations of the HAP model against the continuum mechanics.

Once the effects of lipid charges on the moduli are verified, the PIs
propose to examine how to use an external electric field to control the
amphiphilic self-assembly in solvent. PI YNY has a track record of
working on electrohydrodynamics of an elastic, inextensible membrane
using both asymptotic analysis~\cite{Nganguia2013_PRE, Young2014_JFM,
Young2015_PoF} and numerical simulations~\cite{Nganguia2015_CiCP}, and
will work with both PI RR and BQ to extend the HAP model to study the
electromechanical effects on the assembly of amphiphile. Results from
this research will yield a quantitative understanding of how to utilize
an electric field to achieve optimal control of assembly of amphiphiles
in solvent.

>>>>

\subsubsection{Electromechanical effects on the dynamic assembly of amphiphiles \label{subsubsec:em_effects}}
In recent experiments~\cite{FaizEtAl2019_SoftMatt}, membrane bending rigidity
was determined as a function of lipid composition from 0 to 100 mol $\%$ of
charged lipids using flicker spectroscopy of the shape fluctuations of a giant
unilamellar vesicle (GUV).
%the bending rigidity is determined as a
%function of lipid composition from 0 to 100 mol $\%$ of charged lipids
%in recent experiments~\cite{FaizEtAl2019_SoftMatt}---
Membrane bending rigidity increases with increasing lipid surface charge,
while decreases with increasing salt concentration in the bulk solution
due to the screening of the lipid surface charge. This
agrees with several theoretical models~\cite{Kralchevsky1996_JCIS,
May1996_JChemPhys, LoubetEtAl2013_PRE} that also assume the quadratic
form of the elastic energy density in the presence of surface charge and
bulk charge~\cite{DuplantierGoldstein1990_PRL, Winterhalter1992_JPC}. As
the electrostatic interaction is non-local in nature, we expect that the
controversy of the HK elastic energy form (see
\S\ref{subsec:specific_aim_1}) would worsen in the presence of
electrostatic interactions and electrokinetics. The PIs will extend
the approaches in \S\ref{subsec:specific_aim_1} to charged lipids to
calculate the bending moduli and compare against the experimental
results in~\cite{FaizEtAl2019_SoftMatt}. We propose to incorporate an
explicit surface charge on each particle boundary $P_i$ and compute the
electrostatic potential as a functional of particle configuration.
Adding the electrostatic forces to the hydrophobic attraction forces
between particles to compute the particle assembly dynamics, we can then
calculate elastic moduli as outlined in \S\ref{subsec:specific_aim_1}.
Results from these proposed calculations will provide further comparisons and
validations of the HAP model against the continuum mechanics.

Once the effects of lipid charges on the moduli are verified, the PIs
propose to examine how to use an external electric field to control the
amphiphilic self-assembly in solvent. PI YNY has a track record of
working on electrohydrodynamics of an elastic, inextensible membrane
using both asymptotic analysis~\cite{Nganguia2013_PRE, Young2014_JFM,
Young2015_PoF} and numerical simulations~\cite{Nganguia2015_CiCP} and
will work with both PIs RR and BQ to extend the HAP model to study the
electromechanical effects on the assembly of amphiphile. Results from
this research will yield a quantitative understanding of how to utilize
an electric field to achieve optimal control of assembly of amphiphiles
in solvent.
